StarCraft Bots and Competitions

### 2016-02-11 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
Add Synonyms, Definition and Cross-References sections

\section{State of the Art Bots for StarCraft}\label{sec:bot}

@@

%\subsection{RTS Bot Architectures}\label{sec:integration}

@@

%\subsection{Individual AI Techniques}\label{sec:techniques}

@@

\section{Recent StarCraft AI Competitions}\label{sec:competition}

@@

\subsection{AIIDE}\label{sec:AIIDE}

\subsubsection{AIIDE 2010.}

@@

\subsubsection{AIIDE 2011.}

@@

\subsubsection{AIIDE 2012.}

@@

\subsubsection{AIIDE 2013.}

@@

\subsubsection{AIIDE 2014.}

@@

\subsubsection{AIIDE 2015.}

@@

\subsection{CIG}
\label{sec:cig2011}

@@

\subsubsection{CIG 2011.}

@@

\subsubsection{First Round}
\label{sec:cig-first-round}

@@

\subsubsection{Final Round}
\label{sec:cig-final-round}

@@

\subsubsection{CIG 2012.}

@@

\subsubsection{CIG 2013.} The CIG 2013 competition was once again
organized by Mike Preuss (TU Dortmund) and Tobias Mahlmann (ITU Copenhagen),
adding Antonio Mora Garc{\'i}a from the Universidad de Granada as
third team member. Whereas the rules and even the participants
to this competition were almost identical to the AIIDE 2013
competition setup, several technical changes were made in comparison
to 2012\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/StarCraft-cig2013}}.
A new competition software was implemented by Tobias but
not completely finished in time, so that the read/write function
that enables learning between games had to be disabled again. 
This is probably the most important difference to the AIIDE competition,
however, as the result provided in table~\ref{tab:cig2013} shows, the effect is
limited. Due to the late availability of the competition software,
only 32 rounds of random robin were played, making 896 games
altogether, and 224 games by each of the 8 submitted bots.

@@

\subsubsection{CIG 2014.}
The CIG 2014 competition was organized by Kyung-Joong Kim, Ho-Chul Cho, and In-Seok Oh of Sejong University. For 2014, the CIG competition used a total of 20 different maps which were unknown to the competitors before the competition started, which was by far the most maps ever used in a Starcraft AI competition and presented a challenge to many of the bots who entered. A total of 4680 games were played which meant that each bot played each other bot 60 times, or 3 times per map. The CIG 2014 competition was held just a few weeks before the AIIDE 2014 competition and so many of the entrants to the competition were identical, and the results definitely showed this. The top 4 bots were all the same as the 2014 AIIDE competition with IceBot coming 1st, Ximp in 2nd, LetaBot in 3rd and AIUR in 4th place. For descriptions of these bots please refer to the AIIDE 2014 competition description as none of the top-finishing bots had any significant changes made.

@@

\subsubsection{CIG 2015.}
There were some significant rule changes to the CIG 2015 competition, which was once organized by members from Sejong University. The most significant rule change was that entrants no longer had to be open source, in an attempt to attract more competitors who may not want to open source their bots. The second rule change was that a single competitor could submit multiple entries to the competition - which caused some controversy among registrants since this introduces the possibility of collusion between entries. Thankfully no such collusion was detected during the competition. The 2015 competition was also not run quite as long as previous competitions with only 2730 games being played in total, or 30 between each bot pairing, 6 between each bot on each of the 5 chosen maps. There were several new Zerg entries to the CIG 2015 competition which ended up finishing in the top three positions, with results very similar to those of the AIIDE 2015 competition. ZZZBot took 1st place, tscmoo-Z (a Zerg bot written by tscmoo) came 2nd, and Overkill came 3rd. For descriptions of these bots and their strategies used please refer to the AIIDE 2015 competition section as the strategies remained largely unchanged between the CIG and AIIDE competitions.

@@

\subsection{SSCAIT}\label{sec:SSCAIT}
The Student StarCraft AI Tournament\footnote{\url{http://sscaitournament.com/}} (SSCAIT) started in 2011 at Comenius University in Bratislava, Slovakia and has been well known for being the Starcraft AI competition with the highest number of total participants. Started as a part of a course in artificial intellignece at Comenius University, initial SSCAIT seasons included several dozen student submissions from this course in addition to submissions from across the globe. 
There are three fundamental differences between SSCAIT and the remaining two conferences:
\begin{enumerate}
  \item SSCAIT is an online-only event. Unlike AIIDE or CIG, it is not co-located with a scientific conference or any other real-world event.
  \item There are two phases of SSCAIT each year: a {\em competitive} phase, lasting for up to three weeks and a {\em sandbox} phase which runs for approximately eleven months each year. In other words, SSCAIT is live at all times with only a few short interruptions.
  \item All the games are publicly {\em streamed live} 24 hours a day. The stream uses a custom observer script \cite{mattsson2015automatic} designed specifically to improve the viewer experience and creates a continuous feedback loop for the participants who can watch their bots play against the others.
\end{enumerate}

\subsubsection{SSCAIT 2011.}
%Taking place in winter of 2011, 
The first SSCAIT tournament was organized by Michal \v{C}ertick\'{y} as part of the {\em ``Introduction to Artificial Intelligence''} course at the Department of Applied Informatics, Comenius University in Bratislava, Slovakia. It was inspired by the media coverage of AIIDE StarCraft AI competition held in 2010, but over the following years it diverged from AIIDE competition's format significantly.

@@

\subsubsection{SSCAIT 2012-2015.}
In 2012, the SSCAIT became a truly international competition with 52 participants from numerous universities including 
UC Berkeley (USA), University of Alberta (CAN), Washington State University (USA), University of Nantes (FRA), University of Grenoble (FRA), New University of Lisbon (POT), Gdansk University of Technology (POL), Ritsumeikan University (JAP), University of Bielefeld (GER), Sofia University (BUL), Comenius University (SVK), University of \v{Z}ilina (SVK) and Technical University in Ko\v{s}ice (SVK), as well as a number of non-student participants.

@@

% \subsection{StarCraft Bot Ladder}\label{sec:ladder}

@@

% \subsection{Adaptation Analysis}

>>>>

\section*{Synonyms}

Real-Time Strategy games; RTS games; StarCraft; Artificial Intelligence; AI; Game
AI; Competition

\section*{Definition}

{\em Real-Time Strategy} (RTS) games  is a sub-genre of strategy games
where  players  need to  build  an  economy (gathering  resources  and
building a  base) and military  power (training units  and researching
technologies)  in order  to defeat  their opponents  (destroying their
army and base).  Artificial Intelligence  (AI) problems related to RTS
games deal  with the  behavior of an  artificial player.   Since 2010,
many international competitions  have been organized to  match AIs, or
bots,  playing to  the RTS  game  StarCraft. This  chapter presents  a
review of all  major international competitions from  2010 until 2015,
and details some competing StarCraft bots.

\section*{State of the Art Bots for StarCraft}\label{sec:bot}

@@

%\subsection*{RTS Bot Architectures}\label{sec:integration}

@@

%\subsection*{Individual AI Techniques}\label{sec:techniques}

@@

\section*{Recent StarCraft AI Competitions}\label{sec:competition}

@@

\subsection*{AIIDE}\label{sec:AIIDE}

\subsubsection*{AIIDE 2010.}

@@

\subsubsection*{AIIDE 2011.}

@@

\subsubsection*{AIIDE 2012.}

@@

\subsubsection*{AIIDE 2013.}

@@

\subsubsection*{AIIDE 2014.}

@@

\subsubsection*{AIIDE 2015.}

@@

\subsection*{CIG}
\label{sec:cig2011}

@@

\subsubsection*{CIG 2011.}

@@

\subsubsection*{First Round}
\label{sec:cig-first-round}

@@

\subsubsection*{Final Round}
\label{sec:cig-final-round}

@@

\subsubsection*{CIG 2012.}

@@

\subsubsection*{CIG 2013.} The CIG 2013 competition was once again
organized by Mike Preuss (TU Dortmund) and Tobias Mahlmann (ITU Copenhagen),
adding Antonio Mora Garc{\'i}a from the Universidad de Granada as
third team member. Whereas the rules and even the participants
to this competition were almost identical to the AIIDE 2013
competition setup, several technical changes were made in comparison
to 2012\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/StarCraft-cig2013}}.
A new competition software was implemented by Tobias but
not completely finished in time, so that the read/write function
that enables learning between games had to be disabled again. 
This is probably the most important difference to the AIIDE competition,
however, as the result provided in table~\ref{tab:cig2013} shows, the effect is
limited. Due to the late availability of the competition software,
only 32 rounds of random robin were played, making 896 games
altogether, and 224 games by each of the 8 submitted bots.

@@

\subsubsection*{CIG 2014.}
The CIG 2014 competition was organized by Kyung-Joong Kim, Ho-Chul Cho, and In-Seok Oh of Sejong University. For 2014, the CIG competition used a total of 20 different maps which were unknown to the competitors before the competition started, which was by far the most maps ever used in a Starcraft AI competition and presented a challenge to many of the bots who entered. A total of 4680 games were played which meant that each bot played each other bot 60 times, or 3 times per map. The CIG 2014 competition was held just a few weeks before the AIIDE 2014 competition and so many of the entrants to the competition were identical, and the results definitely showed this. The top 4 bots were all the same as the 2014 AIIDE competition with IceBot coming 1st, Ximp in 2nd, LetaBot in 3rd and AIUR in 4th place. For descriptions of these bots please refer to the AIIDE 2014 competition description as none of the top-finishing bots had any significant changes made.

@@

\subsubsection*{CIG 2015.}
There were some significant rule changes to the CIG 2015 competition, which was once organized by members from Sejong University. The most significant rule change was that entrants no longer had to be open source, in an attempt to attract more competitors who may not want to open source their bots. The second rule change was that a single competitor could submit multiple entries to the competition - which caused some controversy among registrants since this introduces the possibility of collusion between entries. Thankfully no such collusion was detected during the competition. The 2015 competition was also not run quite as long as previous competitions with only 2730 games being played in total, or 30 between each bot pairing, 6 between each bot on each of the 5 chosen maps. There were several new Zerg entries to the CIG 2015 competition which ended up finishing in the top three positions, with results very similar to those of the AIIDE 2015 competition. ZZZBot took 1st place, tscmoo-Z (a Zerg bot written by tscmoo) came 2nd, and Overkill came 3rd. For descriptions of these bots and their strategies used please refer to the AIIDE 2015 competition section as the strategies remained largely unchanged between the CIG and AIIDE competitions.

@@

\subsection*{SSCAIT}\label{sec:SSCAIT}
The Student StarCraft AI Tournament\footnote{\url{http://sscaitournament.com/}} (SSCAIT) started in 2011 at Comenius University in Bratislava, Slovakia and has been well known for being the Starcraft AI competition with the highest number of total participants. Started as a part of a course in artificial intellignece at Comenius University, initial SSCAIT seasons included several dozen student submissions from this course in addition to submissions from across the globe. 
There are three fundamental differences between SSCAIT and the remaining two conferences:
\begin{enumerate}
  \item SSCAIT is an online-only event. Unlike AIIDE or CIG, it is not co-located with a scientific conference or any other real-world event.
  \item There are two phases of SSCAIT each year: a {\em competitive} phase, lasting for up to three weeks and a {\em sandbox} phase which runs for approximately eleven months each year. In other words, SSCAIT is live at all times with only a few short interruptions.
  \item All the games are publicly {\em streamed live} 24 hours a day. The stream uses a custom observer script \cite{mattsson2015automatic} designed specifically to improve the viewer experience and creates a continuous feedback loop for the participants who can watch their bots play against the others.
\end{enumerate}

\subsubsection*{SSCAIT 2011.}
%Taking place in winter of 2011, 
The first SSCAIT tournament was organized by Michal \v{C}ertick\'{y} as part of the {\em ``Introduction to Artificial Intelligence''} course at the Department of Applied Informatics, Comenius University in Bratislava, Slovakia. It was inspired by the media coverage of AIIDE StarCraft AI competition held in 2010, but over the following years it diverged from AIIDE competition's format significantly.

@@

\subsubsection*{SSCAIT 2012-2015.}
In 2012, the SSCAIT became a truly international competition with 52 participants from numerous universities including 
UC Berkeley (USA), University of Alberta (CAN), Washington State University (USA), University of Nantes (FRA), University of Grenoble (FRA), New University of Lisbon (POT), Gdansk University of Technology (POL), Ritsumeikan University (JAP), University of Bielefeld (GER), Sofia University (BUL), Comenius University (SVK), University of \v{Z}ilina (SVK) and Technical University in Ko\v{s}ice (SVK), as well as a number of non-student participants.

@@

\section*{Cross References}
In the Springer Encyclopedia of Computer Graphics an Games volume 1:
\begin{itemize}
\item  Santiago Ontañón,  Gabriel Synnaeve,  Alberto Uriarte,  Florian
  Richoux, David Churchill and Mike Preuss, {\it RTS AI: Problems and Techniques}.
\item Kazuki Yoshizoe and Martin Mueller, {\it Computer Go}.
\end{itemize}

% \subsection*{StarCraft Bot Ladder}\label{sec:ladder}

@@

% \subsection*{Adaptation Analysis}
